Dynamical modeling of tidal streams

### 2013-11-20 tex/ms.tex
streams: change t_0

A detail that is ignored in \equationname~(\ref{eq:aadfsimple}) is
that the uniform prior on $\Delta t$ should only have support for
$\Delta t > 0$, \ie, for times in the past, which introduces an
additional factor of $[1+\mathrm{erf}(t_0)]$, with
\[ t_0 = \frac{\sqrt{\sum_{R,\phi,Z}\Delta
  \veco_i^2}}{\sqrt{2}\,\sigma_\theta}\,\frac{\sum_{R,\phi,Z} \Delta
  \veco_i\Delta \veca_i}{\sum_{R,\phi,Z}\Delta \veco_i^2}\,.\] Because
the second factor on the right-hand side is the best guess for $\Delta
t_i$, if this is large and negative (\ie, the star was stripped
\emph{in the future}), the probability of the star being stripped from
the progenitor is strongly suppressed. Only when it appears that the
star was only recently stripped with $\Delta t_i$ negative, but
$\approx \sigma_\theta/\sqrt{\sum_{R,\phi,Z}\Delta \veco_i^2}$, is the
suppression for negative stripping times less.

>>>>

A detail that is ignored in \equationname~(\ref{eq:aadfsimple}) is
that the uniform prior on $\Delta t$ should only have support for
$\Delta t > 0$, \ie, for times in the past, which introduces an
additional factor of $[1+\mathrm{erf}(a_0)]$, with
\[ a_0 = \frac{\sqrt{\sum_{R,\phi,Z}\Delta
  \veco_i^2}}{\sqrt{2}\,\sigma_\theta}\,\frac{\sum_{R,\phi,Z} \Delta
  \veco_i\Delta \veca_i}{\sum_{R,\phi,Z}\Delta \veco_i^2}\,.\] Because
the second factor on the right-hand side is the best guess for $\Delta
t_i$, if this is large and negative (\ie, the star was stripped
\emph{in the future}), the probability of the star being stripped from
the progenitor is strongly suppressed. Only when it appears that the
star was only recently stripped with $\Delta t_i$ negative, but
$\approx \sigma_\theta/\sqrt{\sum_{R,\phi,Z}\Delta \veco_i^2}$, is the
suppression for negative stripping times less.
